---
title: "Tentative Migration Reading List"
author: "Andrea Miranda-Gonzalez"
date: "September 2020"
output: 
  pdf_document:
    toc: true
    keep_tex: true
    fig_caption: yes
    latex_engine: xelatex
    #template: "G:/Mi unidad/2020/Oral Exams/oral_exam_notes/svm-latex-syllabus.tex"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
header-includes:
   - \linespread{1.05}

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='pdf')

library(RefManageR)
# library(knitcitations)
# library(rcrossref)

bib <- ReadBib("references_migration.bib",
                check=F)
myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=FALSE, max.names = 20, sorting="ydnt")
```


# **Why people migrate?** 
## *Early economic theories*

```{r, echo = FALSE, results="asis"} 
bib[c("ravenstein1889laws","sjaastad1962costs","lee1966theory","todaro1969model","zelinsky1971hypothesis","harris1970migration","stark1989relative","stark1985new","borjas1989economic","chiswick1999immigrants")]
```

## *Contemporary sociological theories*

```{r, echo = FALSE, results="asis"} 
bib[c("massey1993theories","sassen1989america","massey1999why","garip2019move","piore1979birds","mckeown2004global","hatton2005global","ryo2013deciding","williams2012migration")]

``` 

## *Role of the State*
```{r, echo = FALSE, results="asis"} 
bib[c("zolberg1999matters","torpey1998coming","boswell2007theorizing","neumayer2005bogus","freeman1995modes","hollifield2014dilemmas","cornelius2005controlling","ruhs2008numbers")]
```    

***
# **How do we observe migration? Data and measurements**
## *Data sources*
```{r, echo = FALSE, results="asis"} 

bib[c("hill1987new","shryock1973methods","massey1995new","kaplan2012interstate","schmertmann1992estimation","bell2003comparing","dumont2005counting","bycroft2006challenges","van2006foreign","nicholson1990hidden","rees2000problems",
"clark1985human","skeldon1990population","beauchemin2014manifesto","zagheni2014inferring","messias2016migration","moed2014bibliometric","hawelka2014geo","zagheni2017leveraging","blumenstock2012inferring","ruggles2014big","hughes2016inferring","weber2015demographic","cesare2018promises")]
```
  
## *Methods*
```{r, echo = FALSE, results="asis"} 

bib[c("bell2015demography","wachter2014essential","yusuf2014methods","rogers2010indirect","bell2015internal","bell2002cross","rees2000problems","rees2017impact","rogers1981model","bernard2017cohort","bernard2014life","bijak2005bayesian","bijak2010forecasting","klabunde2016decision","riosmena2016potential","liu2016prospects")]
```

## *Comments on type of methods: quantitative vs qualitative methods*
```{r, echo = FALSE, results="asis"} 
bib[c("bloemraad2007puzzles","zenteno1999especificidad","massey2000validation","willekens2016international")]

```  
   Handbook of research methods in migration
   

***
# **Demographic processes within migration**
## *Migration and fertility*
```{r, echo = FALSE, results="asis"} 
bib[c("parrado2011high","choi2012international","friedlander1983demographic",
"davis2010effects","kulu2005migration")]
```

## *Migration, health and mortality*
```{r, echo = FALSE, results="asis"} 
bib[c("palloni2004paradox","riosmena2017explaining")]
```

## *Migration, aging and the life course*
```{r, echo = FALSE, results="asis"} 
bib[c("litwak1987migration","vega2019reasons","acevedo2012integrating","ruiz2013hispanic","feliciano2005educational")]

```

***
# **Types of migration **
## *International and internal migration*
```{r, echo = FALSE, results="asis"} 
bib[c("mayda2010international","hanson2010great","greenwood1997internal","johnson2017frozen","flippen2013relative")]
```  

## *Urbanization*
```{r, echo = FALSE, results="asis"} 
bib[c("hall2015neighborhood","clark1991residential","davis1955origin")]
``` 

## *Forced migration* 

```{r, echo = FALSE, results="asis"} 
bib[c("lee2002enforcing","hamlin2012symbolic","neumayer2004asylum","riosmena2018climate","schon2019motivation","zolberg1986international","nwokeji2001african","horowitz1991victims")]
```  

***
# **Integration/Assimilation**
```{r, echo = FALSE, results="asis"} 
bib[c("gordon1964assimilation","alba2009remaking","kasinitz2009inheriting","perlmann2005italians","alba2014mexican","lee2015asian","brown2006assimilation")]
```

## *Segmented assimilation*
```{r, echo = FALSE, results="asis"} 
bib[c("gans1992second","portes1993new","portes2009adaptation","telles2008generations","xie2011social","haller2011dreams","soehl2020social")]
```  

## *Role of legal status*
```{r, echo = FALSE, results="asis"} 
bib[c("sigona2012have","abrego2006can","gonzales2011learning","gleeson2010labor","menjivar2012legal","dreby2012burden","brown2011refugees","menjivar2006liminal","yoshikawa2011immigrants","dreby2015everyday","gonzales2016lives","bean2015parents","cainkar2009homeland")]
```

## *Undocumented migration*
```{r, echo = FALSE, results="asis"} 
bib[c("donato2011we","massey2016border","amuedo2014intended","ngai2003strange","de2004legal","de2002migrant","nevins2002operation")]
```
***

# **Important characteristic of migrants**

## *Gender* 
```{r, echo = FALSE, results="asis"} 
bib[c("pedraza1991women","hondagneu2000feminism","lutz2010gender","mahler2006gender","pessar2003transnational","cantu2009sexuality","acosta2008lesbianas","kunz2008remittances","semyonov2005labor","cerrutti2001auspices","curran2003engendering","kanaiaupuni2000reframing","massey2006international")]  
```

## *Children*
```{r, echo = FALSE, results="asis"} 
bib[c("huijsmans2011child","dobson2009unpacking","white2011children","donato2015children","donato2011migration","dreby2012burden")]

```  

## *The family*
```{r, echo = FALSE, results="asis"} 
bib[c("mincer1978family","boyd1989family","bielby1992will","shauman2007family","shauman2010gender","cooke2009longitudinal","raghuram2004difference","kulu2007family","cooke2008migration","lacroix2019life","de2008family","nobles2013migration","nobles2011parenting","gao2010impact","yeung2016left","de1993family","de2008family","desai2008negotiated","de2010migration")]
```

## *Networks*
```{r, echo = FALSE, results="asis"} 
bib[c("portes1998social","massey1993theories","granovetter1973","wilson1998weak","garip2008social","liu2013migrant","palloni2001social","mouw2006estimating","aguilera2003social","massey2011social","montgomery1991","davis2002domestic","fussell2004limits","delechat2001international","curran2003engendering","kanaiaupuni2000reframing","creighton2013migration")]
```

# **Mexico-US migration**
See syllabus for ''Teorias sociales de la migracion''. Also need to talk about return migration and circular migration.

```{r, echo = FALSE, results="asis"} 
bib[c("massey1997s","fussell2004sources","davis2002domestic","hill2005mexico","roberts1997china","durand2017")]

```



